---
title: "Bootstrapping"
author: "Jasmine Zhang"
date: "2023-11-16"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)
set.seed(1)
```

## Generate a relevant sample

```{r}
n_samp = 250
#constant variance 
sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error)

#non constant variance 
sim_df_nonconst = sim_df_const |> 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error)
```

fit some linear models: lm assumes constant variance

```{r}
sim_df_const |> 
  lm(y~x, data = _) |> 
  broom::tidy()

sim_df_nonconst |> 
  lm(y~x, data = _) |> 
  broom::tidy()
```

solve the case when the variance is not constant 

## Draw and analyze a bootstrap sample

```{r}
boot_sample = function(df){
  sample_frac(df, replace = TRUE)
}
```

Lets see how it works

```{r}
sim_df_nonconst |> 
  boot_sample() |> 
  ggplot(aes(x=x, y=y))+
  geom_point(alpha = 0.5)+
  stat_smooth(method = "lm") #change when bootstrap sample changes 
```

## draw multiple bootstrap samples and analyze them

```{r}
boot_straps = tibble(strap_number = 1:100) |> 
  mutate(strap_sample = map(strap_number, \(i) boot_sample(sim_df_nonconst)))
boot_straps |> 
  pull(strap_sample) |> 
  nth(1) |> 
  arrange(x)
```

Now do the `lm` fit

```{r}
boot_results = boot_straps |> 
  mutate(models = map(strap_sample, \(df) lm(y~x, data = df)),
         results = map(models, broom::tidy)) |> 
  select(strap_number, results) |> 
  unnest(results)
```

try to summarize these results: get a bootstrap SE

```{r}
boot_results |> 
  group_by(term) |> 
  summarize(
    se = sd(estimate)
  )
```

Look at the distribution

```{r}
boot_results |> 
  filter(term == "x") |> 
  ggplot(aes(x = estimate)) + 
  geom_density() 
```

## Airbnb dataset

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  drop_na(price, stars) |> 
  select(price, stars, borough, neighborhood, room_type)
```

lets fit a regression of `price` on other variables and look at residuals

```{r}
airbnb_fit = nyc_airbnb |> 
  lm(price ~ stars+room_type+borough, data = _)

#residuals
nyc_airbnb |> 
  modelr::add_residuals(airbnb_fit) |> 
  ggplot(aes(x = stars, y = resid)) + geom_point() #residual very skewed 
```

run a bootstrap on this whole thing to get estimates for the effect of `stars` on `price`

```{r}
manhattan_df = nyc_airbnb |> 
  filter(borough == "Manhattan") 
boot_results = tibble(strap_number = 1:1000) |> 
  mutate(strap_sample = map(strap_number, \(i) boot_sample(manhattan_df)),
         models = map(strap_sample, \(df) lm(price~ stars+room_type, data = df)),
         results = map(models, broom::tidy)) |> 
  select(strap_number, results) |> 
  unnest(results)
```

```{r}
boot_results |> 
  filter(term == "stars") |> 
  ggplot(aes(x = estimate)) + geom_density()
#show dist of estimate of stars as a predictor of price 
```

